\bf Estimating the number of clusters using cross-validation

### 2018-03-09 cvclust.tex
add response about k

Our correlation correction is not backed by a rigorous theoretical
justification. However, the simulations and empirical validation in
Sections~\ref{sec:simulations} and~\ref{sec:empirical-validation}
demonstrate the effectiveness of our ad-hoc adjustment procedure.

>>>>

Our correlation correction is not backed by a rigorous theoretical
justification. Further, since our initial estimate $\hat k_0$ tends to
over-estimate the true number of clusters, our covariance estimate $\hat
\Sigma$ will often be biased. Fortunately, we do not need to estimate $\Sigma$
with high accuracy. For our correction to be useful, we only need $\hat
\Sigma^{-1/2}$ to have lower within-cluster correlation than the raw data. In
our simulations and in our empirical validation study in
Sections~\ref{sec:simulations} and~\ref{sec:empirical-validation} we
demonstrate that despite its theoretical shortcoming, our ad-hoc correlation
adjustment often performs well in practice.
